Supporting Information:\\ Accurate Binding of Sodium and Calcium to a POPC Bilayer by Effective Inclusion of Electronic Polarization

### 2018-03-20 Manuscript/SI.tex
Second submission to J. Phys. Chem. B

\begin{figure}[!h]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OP.pdf}
  \caption{\label{scaledCHARMM}
    Changes of the headgroup order parameters as a function of NaCl (left) and CaCl$_2$ (right)
    from simulations with CHARMM36 \cite{klauda10}, simulations with ECC-CHARMM36 parameters and experiments \cite{akutsu81,altenbach84}. 
    CHARMM36 force field parameters for simulations with and without NaCl were taken from CHARMM-GUI \cite{lee15}.
    These were ran 320 ns and 280 ns, respectively, and the first 100 ns was omitted from the analysis.
    Results for CHARMM36 with CaCl$_2$ were calculated from the last 100 ns from the data available at Ref.~\citenum{charmmPOPC450mMCaClfiles}.
    ECC-CHARMM36 simulations with NaCl and CaCl$_2$ were ran 260 ns and 600 ns, respectively, and the first 100 ns were omitted from the analysis.
    Sodium, calcium, and chloride ions were modeled as ECC-ions in these simulations with parameters from Refs. \citenum{martinek17, Pluharova2014}.
    All the other simulation parameters in simulations in this figure were equal to the available dataset at Ref.~\citenum{charmmPOPC450mMCaClfiles}.
    The temperature in all simulations was set to 310 K.
    The simulation data is available at Refs. \citenum{charmm36popcT310K,charmm36popc940mMNaClT310K,ECCcharmm36popcT310K,ECCcharmm36popc940mMNaClT310K,ECCcharmm36popc450mMCaClT310K}.
  }
\end{figure}

\newpage
\begin{figure}[!h]
  \centering
  \includegraphics[width=10.0cm]{../Fig/density2.pdf}
  \caption{\label{scaledCHARMMdensity}
    Number density profiles along membrane normal from CHARMM36 \cite{klauda10} and ECC-CHARMM36 models with NaCl and CaCl$_2$.
    The values for the relative surface excess are also shown.
  }
\end{figure}

\newpage
\begin{figure}[!h]
  \centering
  \includegraphics[width=16.0cm]{../Fig/contacts_ca.pdf}
  \caption{\label{scaledCHARMMcontacts}
    Number of bound Ca$^{2+}$ during simulations.
  }
\end{figure}

>>>>

\begin{figure}[!h]
  \centering
  \includegraphics[width=16.0cm]{../Fig/OP.pdf}
  \caption{\label{scaledCHARMM}
    Changes of the headgroup order parameters as a function of NaCl (left) and CaCl$_2$ (right)
    from simulations with CHARMM36 \cite{klauda10}, simulations with ECC-CHARMM36 parameters and experiments \cite{akutsu81,altenbach84}. 
    CHARMM36 force field parameters for simulations with and without NaCl were taken from CHARMM-GUI \cite{lee15}.
    These were ran 320 ns and 280 ns, respectively, and the first 100 ns was omitted from the analysis.
    Results for CHARMM36 with CaCl$_2$ were calculated from the last 100 ns from the data available at Ref.~\citenum{charmmPOPC450mMCaClfiles}.
    ECC-CHARMM36 simulations with NaCl and CaCl$_2$ were ran 260 ns and 600 ns, respectively, and the first 100 ns were omitted from the analysis.
    Sodium, calcium, and chloride ions were modeled as ECC-ions in these simulations with parameters from Refs. \citenum{martinek17, Pluharova2014}.
    All the other simulation parameters in simulations in this figure were equal to the available dataset at Ref.~\citenum{charmmPOPC450mMCaClfiles}.
    The temperature in all simulations was set to 310 K.
    The simulation data is available at Refs.~\citenum{charmm36popcT310K,charmm36popc940mMNaClT310K,ECCcharmm36popcT310K,ECCcharmm36popc940mMNaClT310K,ECCcharmm36popc450mMCaClT310K}.
  }
\end{figure}

\newpage
\begin{figure}[!h]
  \centering
  \includegraphics[width=10.0cm]{../Fig/density2.pdf}
  \caption{\label{scaledCHARMMdensity}
    Number density profiles along membrane normal from CHARMM36 \cite{klauda10} and ECC-CHARMM36 models with NaCl and CaCl$_2$.
    The values for the relative surface excess are also shown. Simulation details are as in Fig. \ref{scaledCHARMM}.
  }
\end{figure}

\newpage
\begin{figure}[!h]
  \centering
  \includegraphics[width=16.0cm]{../Fig/contacts_ca.pdf}
  \caption{\label{scaledCHARMMcontacts}
    Number of bound Ca$^{2+}$ during simulations. The data for CHARMM36 is taken directly from Refs. \citenum{catte16,charmmPOPC450mMCaClfiles,githubIONpaper} 
  }
\end{figure}
